\thesistitle

### 2019-07-15 sections/research.tex
AST Filtering

Building the clone graph consists of walking the AST in-order for each declaration and statement. For each declaration/statement found, we map the following relations:
\begin{itemize}
  \item The declaration/statement preceding it.
  \item The declaration/statement following.
  \item The last \textbf{preceding} declaration/statement with which it is cloned.
\end{itemize}
We do not create a separate graph for each class file, so the statement/declaration preceding or following could be in a different file. While mapping these relations, we maintain a hashed map containing the last occurrence of each unique statement. This map is used to efficiently find out whether a statement is cloned with another. An example of such a graph is displayed in figure \ref{fig:clonegraphsimple}.

>>>>

\paragraph{Filtering the AST}
As a first step towards building the clone graph, we preprocess the AST to decide which AST nodes should become part of the clone graph. We filter the following types of nodes:
\begin{itemize}
  \item \textbf{Expressions: }The smallest entity in the clone graph is a Statement. Because of that, we filter out all expressions.
  \item \textbf{Package declaration and import statements: }These are omitted by most clone detection tools, as clones in import statements hold limited valuable information.
  \item \textbf{Modifiers: }The clone graphs' nodes consist of only declarations and statements. Modifiers are part of the declarations, so they are not considered separately.
\end{itemize}

\paragraph{Building the clone graph}
Building the clone graph consists of walking the AST in-order for each declaration and statement. For each declaration/statement found, we map the following relations:
\begin{itemize}
  \item The declaration/statement preceding it.
  \item The declaration/statement following.
  \item The last \textbf{preceding} declaration/statement with which it is cloned.
\end{itemize}
We do not create a separate graph for each class file, so the statement/declaration preceding or following could be in a different file. While mapping these relations, we maintain a hashed map containing the last occurrence of each unique statement. This map is used to efficiently find out whether a statement is cloned with another. An example of such a graph is displayed in figure \ref{fig:clonegraphsimple}.
